---
title: "Repro Samples Method — Short Course Demo"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  message = FALSE,
  warning = FALSE,
  cache   = TRUE,
  fig.width  = 8,
  fig.height = 5
)
```

```{r load-functions, cache=FALSE}
# Works whether running interactively (wd = repro_demo/) or knitting (wd = demo/)
base_path <- if (file.exists("gmm/functions.R")) "." else ".."
source(file.path(base_path, "gmm/functions.R"))
source(file.path(base_path, "hd_linear/functions.R"))

library(ggplot2)
library(mixAK)   # for SLC data and data(SLC)
```

---

# Part 1: Gaussian Mixture Model with Unknown Number of Components

**Goal:** Given i.i.d. data $Y_i$ from a $K_0$-component Gaussian mixture, construct a
confidence set for the unknown discrete parameter $K_0$.

**Challenge:** $K_0$ is a discrete integer — CLT-based methods cannot form valid CIs
directly. The repro samples approach bypasses this by working with the generative model.

---

## 1.1 Real Data — SLC Dataset

190 red-blood-cell sodium–lithium countertransport (SLC) measurements.
Earlier work (Roeder 1994; Chen et al. 2012) analyzed this with GMMs.

```{r slc-load}
data(SLC)
ys_real <- SLC$SLC
cat("n =", length(ys_real), "  mean =", round(mean(ys_real), 3),
    "  sd =", round(sd(ys_real), 3))
```

```{r slc-plot, fig.cap="SLC data histogram with GMM density fits for K = 2, 3, 4"}
# Fit K = 2, 3, 4 via EM
fit_list <- lapply(2:4, function(k) GMM(matrix(ys_real), k, seed = 42))

# Build density curves
x_seq <- seq(min(ys_real) - 0.05, max(ys_real) + 0.05, length.out = 500)
density_df <- do.call(rbind, lapply(seq_along(fit_list), function(j) {
  k   <- j + 1
  fit <- fit_list[[j]]
  w   <- as.vector(fit$weights)
  mu  <- as.vector(fit$centroids)
  sig <- sqrt(as.vector(fit$covariance_matrices))
  dens <- rowSums(sapply(seq_len(k), function(i) w[i] * dnorm(x_seq, mu[i], sig[i])))
  data.frame(x = x_seq, density = dens, K = factor(paste0("K = ", k)))
}))

ggplot() +
  geom_histogram(aes(x = ys_real, y = after_stat(density)),
                 bins = 30, fill = "steelblue", alpha = 0.4, color = "white") +
  geom_line(data = density_df, aes(x = x, y = density, color = K), linewidth = 1.1) +
  scale_color_manual(values = c("K = 2" = "#e74c3c", "K = 3" = "#2ecc71", "K = 4" = "#9b59b6")) +
  labs(title = "SLC Data: Histogram and Fitted GMM Densities",
       x = "SLC Measurement", y = "Density", color = "# Components") +
  theme_bw(base_size = 14)
```

Visually, it is not clear whether $K_0 = 2, 3$, or $4$.
The repro samples method will give a formal 95% confidence set.

---

## 1.2 Simulation Data — Synthetic K₀ = 4

To clearly demonstrate the method we use a synthetic 4-component GMM with
well-separated components, so the true structure is unambiguous.

```{r slc-sim-setup}
# Four clearly separated components, equal weights
K0_sim <- 4
mu0    <- c(-4, -1, 2, 5)
sigma0 <- c(0.8, 0.8, 0.8, 0.8)
p0     <- c(0.25, 0.25, 0.25, 0.25)

cat("Component weights:  ", p0, "\n")
cat("Component means:    ", mu0, "\n")
cat("Component std devs: ", sigma0, "\n")
```

**Generative model:**
$$Y_i = \sum_{k=1}^{K_0} m_{ik}(\mu_k + \sigma_k U_i), \quad U_i \overset{iid}{\sim} N(0,1)$$
where $M = (m_{ik}) \in \{0,1\}^{n \times K_0}$ is the (unobserved) membership matrix.

```{r slc-sim-generate}
set.seed(2025)
n_sim <- 200

M_sim  <- factor(sample(1:K0_sim, n_sim, replace = TRUE, prob = p0))
M_mat  <- model.matrix(~ M_sim - 1)
U_rel  <- rnorm(n_sim)
ys_obs <- as.vector(M_mat %*% mu0 + diag(U_rel) %*% M_mat %*% sigma0)

cat("Simulated data:  n =", n_sim, "  true K₀ =", K0_sim)
```

```{r slc-sim-plot, fig.cap="Simulated data (K₀ = 4) with true density — four peaks clearly visible"}
x_seq_sim <- seq(min(ys_obs) - 1, max(ys_obs) + 1, length.out = 500)
true_dens_df <- data.frame(
  x = x_seq_sim,
  density = rowSums(sapply(1:K0_sim, function(k)
    p0[k] * dnorm(x_seq_sim, mu0[k], sigma0[k])))
)

ggplot() +
  geom_histogram(aes(x = ys_obs, y = after_stat(density)),
                 bins = 35, fill = "#3498db", alpha = 0.4, color = "white") +
  geom_line(data = true_dens_df, aes(x = x, y = density),
            color = "#e74c3c", linewidth = 1.3) +
  labs(title = "Simulated GMM Data (true K₀ = 4)",
       subtitle = "Red curve: true density  |  Four peaks are clearly visible",
       x = "Y", y = "Density") +
  theme_bw(base_size = 14)
```

---

## 1.3 Repro Sampling — Core Steps

### Observed K estimate (BIC)

```{r gmm-khat}
K_h_grid <- 1:8
set.seed(2025)
K_hat_obs <- Estimate_K(ys_obs, K_grid = K_h_grid, seed_local = 2025)$K_hat
cat("BIC-selected K on observed data: K_hat =", K_hat_obs)
```

---

### Step 1 · Fisher Inversion → Candidate Set $\widehat{Y}(y_{obs})$

For each repro copy $\mathbf{u}^* \sim N(\mathbf{0}, \mathbf{I}_n)$, we solve

$$(\tau^*, M^*) = \arg\min_{(\tau, M_\tau)} \min_{\mu, \bar{\sigma}} \;
n \log\!\left(\frac{\|y_{obs} - M_\tau \mu - \bar{\sigma}\, u^*\|^2 + 1}{n}\right)
+ \lambda \cdot \tau \log n$$

by fitting a mixture linear regression $y_{obs} \sim u^*$ with `flexmix`.

```{r gmm-candidate, cache=TRUE, results='hide'}
set.seed(2025)
repro_M_size <- 30          # number of u* draws for candidate set
invisible(capture.output(
  M_candidate <- Get_M_u_BIC_modified(ys_obs, K_h_grid, repro_M_size = repro_M_size)
))

K_cand_vec   <- apply(M_candidate, 2, function(v) length(unique(v)))
n_unique_M   <- ncol(M_candidate)
```

```{r gmm-candidate-print}
cat("Repro draws:", repro_M_size, "\n")
cat("Unique candidate M's:", n_unique_M, "\n")
cat("K values in candidate set:", sort(unique(K_cand_vec)), "\n")
```

```{r gmm-candidate-plot, fig.cap="Distribution of K in candidate set (Fisher inversion)"}
cand_df <- data.frame(K = K_cand_vec)
ggplot(cand_df, aes(x = factor(K))) +
  geom_bar(fill = "#2980b9", color = "white", width = 0.6) +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5, size = 5) +
  labs(title = "Candidate Set: How Many Times Each K Appeared",
       subtitle = paste("Each bar = one u* draw leading to that K via modified BIC"),
       x = "K (number of components)", y = "Count") +
  theme_bw(base_size = 14)
```

---

### Step 2 · Nuclear Mapping $\widetilde{T}(y_{obs}, \tau, M_\tau)$

For each candidate $(K, M)$, generate repro samples $Y' = M \mathbf{a}(y_{obs}) + \text{diag}(M \mathbf{b}(y_{obs}))\, \mathbf{c}(U')$
and compute the nuclear statistic:

$$\widetilde{T}(y_{obs}, K, M) = \sum_{\bar{K}: \hat{P}_{Y'}(\bar{K}) > \hat{P}_{Y'}(K_{obs})} \hat{P}_{Y'}(\bar{K})$$

```{r gmm-nuclear, cache=TRUE, results='hide'}
set.seed(2025)
repro_size    <- 100    # Monte-Carlo size for nuclear mapping

unique_K_vals  <- sort(unique(K_cand_vec))
nuclear_per_K  <- numeric(length(unique_K_vals))

for (j in seq_along(unique_K_vals)) {
  k_j    <- unique_K_vals[j]
  idx_j  <- which(K_cand_vec == k_j)
  nuclear_per_K[j] <- min(sapply(idx_j, function(i) {
    invisible(capture.output(
      nuc <- Get_nuclear_M(ys_obs, as.vector(M_candidate[, i]),
                           K_hat_obs, repro_size, K_h_grid,
                           seed_local_repro = 2025)
    ))
    nuc$Nuclear_values_2
  }))
}

nuclear_df <- data.frame(K = unique_K_vals, Nuclear = round(nuclear_per_K, 4))
knitr::kable(nuclear_df,
             col.names = c("K (candidate)", "Nuclear statistic  min_M T̃"),
             caption = "Nuclear statistic per candidate K (smaller = more consistent with data)")
```

---

### Step 3 · 95% Confidence Set for $K_0$

$$\Xi_{0.95}(y_{obs}) = \{K : \min_{M_K} \widetilde{T}(y_{obs}, K, M_K) \le 0.95\}$$

```{r gmm-confidence-set}
alpha <- 0.05

# skip_K_obs = TRUE: K_hat_obs is always included (matches original code logic).
# Repro sampling only needs to judge whether *other* K values are also plausible.
K_confidence_set <- unique(sort(c(
  K_hat_obs,                                      # always in CS
  nuclear_df$K[nuclear_df$Nuclear <= (1 - alpha)] # others passing nuclear test
)))

nuclear_df$In_CS <- ifelse(
  nuclear_df$K == K_hat_obs,
  "✓ K̂_obs (auto-included)",
  ifelse(nuclear_df$Nuclear <= (1 - alpha), "✓ In 95% CS", "✗ Excluded")
)
knitr::kable(nuclear_df,
             col.names = c("K", "Nuclear statistic", "In Confidence Set"),
             caption = "95% Confidence set for K₀  (K̂_obs is always included)")

cat("K̂_obs (BIC on data):", K_hat_obs, "\n")
cat("95% Confidence Set for K₀:", K_confidence_set, "\n")
cat("True K₀ =", K0_sim, "  →  Covered:", K0_sim %in% K_confidence_set, "\n")
```

```{r gmm-cs-plot, fig.cap="Nuclear statistics with 95% threshold"}
ggplot(nuclear_df, aes(x = factor(K), y = Nuclear, fill = In_CS)) +
  geom_col(width = 0.6, color = "white") +
  geom_hline(yintercept = 1 - alpha, linetype = "dashed",
             color = "#e74c3c", linewidth = 1.1) +
  annotate("text", x = 0.7, y = 1 - alpha + 0.02,
           label = "95% threshold", color = "#e74c3c", size = 4, hjust = 0) +
  scale_fill_manual(values = c("✓ K̂_obs (auto-included)" = "#2980b9",
                               "✓ In 95% CS"             = "#27ae60",
                               "✗ Excluded"              = "#e74c3c")) +
  labs(title = "Nuclear Statistic per Candidate K",
       subtitle = "K values below the dashed line are in the 95% confidence set",
       x = "K (number of components)", y = "Nuclear statistic", fill = NULL) +
  theme_bw(base_size = 14)
```

---

## 1.4 Apply to Real SLC Data

```{r gmm-slc-real, cache=TRUE, results='hide'}
set.seed(2025)
invisible(capture.output(
  M_cand_real <- Get_M_u_BIC_modified(ys_real, K_h_grid, repro_M_size = 30)
))
K_cand_real   <- apply(M_cand_real, 2, function(v) length(unique(v)))
K_hat_real    <- Estimate_K(ys_real, K_h_grid, seed_local = 2025)$K_hat

unique_K_real <- sort(unique(K_cand_real))
nuclear_real  <- numeric(length(unique_K_real))

for (j in seq_along(unique_K_real)) {
  k_j   <- unique_K_real[j]
  idx_j <- which(K_cand_real == k_j)
  nuclear_real[j] <- min(sapply(idx_j, function(i) {
    invisible(capture.output(
      nuc <- Get_nuclear_M(ys_real, as.vector(M_cand_real[, i]),
                           K_hat_real, 80, K_h_grid, 2025)
    ))
    nuc$Nuclear_values_2
  }))
}

cs_real <- unique_K_real[nuclear_real <= 0.95]
cat("Real SLC data — 95% Confidence Set for K₀:", cs_real, "\n")
```



---

# Part 2: High-Dimensional Linear Regression

**Goal:** Given $n = 50$ observations, $p = 1000$ predictors, only 3 are true signals.
Construct (a) a **model confidence set** for the true sparsity pattern $\tau_0$ and
(b) **coefficient confidence intervals** accounting for model selection uncertainty.

**Model:** $y_{obs} = X_{\tau_0} \beta_{\tau_0} + \sigma_0 u^{rel}$, $\; u^{rel} \sim N(0, I_n)$

---

## 2.1 Simulation Data — Model M1

```{r hlm-data}
set.seed(42)
n <- 50
p <- 1000
rho <- 0.5
sigma_true <- 1
beta_true <- rep(0, p)
beta_true[c(1, 2, 3)] <- c(3, 2, 1.5)

Sigma <- rho^(abs(outer(1:p, 1:p, "-")))
X <- MASS::mvrnorm(n, rep(0, p), Sigma)
Y <- X %*% beta_true + rnorm(n, sd = sigma_true)

cat("True nonzero variables: {1, 2, 3}\n")
cat("True coefficients:       β₁=3, β₂=2, β₃=1.5\n")
cat("Data dimensions:         n =", n, ", p =", p, "\n")
```

```{r hlm-data-plot, fig.cap="Response Y vs the three true predictors", fig.height=4}
scatter_df <- data.frame(
  Y  = rep(Y, 3),
  X_val = c(X[, 1], X[, 2], X[, 3]),
  Var = rep(c("X₁  (β=3)", "X₂  (β=2)", "X₃  (β=1.5)"), each = n)
)

ggplot(scatter_df, aes(x = X_val, y = Y)) +
  geom_point(alpha = 0.6, color = "#2980b9") +
  geom_smooth(method = "lm", se = FALSE, color = "#e74c3c", linewidth = 1.1) +
  facet_wrap(~ Var, scales = "free_x") +
  labs(title = "Response Y vs True Signal Predictors",
       x = "Predictor value", y = "Y") +
  theme_bw(base_size = 13)
```

---

## 2.2 Repro Sampling — Core Steps

### Step 1 · Fisher Inversion → Candidate Model Set $S^{(d)}$

For each repro copy $u^*_b \sim N(0, I_n)$, solve:
$$\hat{h}_b = \arg\min_{\tau} \min_{\beta, \sigma}
\|y_{obs} - X_\tau \beta_\tau - \sigma u^*_b\|^2 + \lambda |\tau|$$

by running **adaptive Lasso** on the augmented design $[X \mid u^*_b]$.
The $u^*$ coefficient's magnitude estimates $\sigma$.

```{r hlm-fisher, cache=TRUE, results='hide'}
set.seed(2025)
d <- 100   # number of repro copies

result <- rps_hlm_inf(
  Y                = Y,
  X                = X,
  rps_size_candidate = d,
  rps_size_modelcs   = 100,
  beta_index         = 1:p,
  intercept          = FALSE,
  u_star_seed        = 2025,
  keep_solution_path = TRUE
)
```

```{r hlm-candidate-summary}
cand_models <- result$candidate_model_list
cat("Fisher inversion: d =", d, "repro draws\n")
cat("Unique candidate models found:", length(cand_models), "\n\n")

# Model sizes
sizes <- sapply(cand_models, length)
cat("Candidate model sizes (# selected variables):\n")
print(sort(sizes))
```

```{r hlm-freq-plot, fig.cap="Variable selection frequency across d=100 repro copies", fig.height=3.5}
# Count how often each variable appears across all repro samples
all_vars <- unlist(result$candidate_model_list)
freq_df  <- as.data.frame(table(Variable = all_vars))
freq_df$Variable <- as.integer(as.character(freq_df$Variable))
freq_df <- freq_df[order(-freq_df$Freq), ]

top_vars <- head(freq_df, 20)
top_vars$is_true <- top_vars$Variable %in% c(1, 2, 3)

ggplot(top_vars, aes(x = reorder(factor(Variable), Freq),
                     y = Freq, fill = is_true)) +
  geom_col(color = "white") +
  coord_flip() +
  scale_fill_manual(values = c("TRUE" = "#e74c3c", "FALSE" = "#7f8c8d"),
                    labels = c("FALSE" = "False positive", "TRUE" = "True signal")) +
  labs(title = "Top-20 Variables by Selection Frequency",
       subtitle = "Red = true signal variables (1, 2, 3)",
       x = "Variable index", y = "Times selected (out of 100 repro copies)", fill = NULL) +
  theme_bw(base_size = 13)
```

---

### Step 2 · Unique Candidate Models

```{r hlm-candidate-table}
cand_table <- data.frame(
  Model_ID     = seq_along(cand_models),
  Variables    = sapply(cand_models, function(m) paste(m, collapse = ", ")),
  Model_Size   = sapply(cand_models, length),
  p_value      = round(result$model_inf$p_value_vector, 4)
)
knitr::kable(cand_table,
             col.names = c("Model", "Selected Variables", "Size |τ|", "p-value"),
             caption = "Candidate models from Fisher inversion, with Fisher-Dempster p-values")
```

---

### Step 3 · Fisher-Dempster Inversion → Model Confidence Set

For each candidate $\tau_b \in S^{(d)}$, compute the **conditional p-value**:

$$\hat{F}_{(w, \tau_b)}\{\hat{T}(y_{obs}, \tau_b)\} =
  \sum_{\tau': \hat{p}_{(w,\tau_b)}(\tau') \le \hat{p}_{(w,\tau_b)}(\hat{T}(y_{obs},\tau_b))} \hat{p}_{(w,\tau_b)}(\tau')$$

The **model confidence set** is $\Gamma_{0.95}^\tau(y_{obs}) = S^{(d)} \cap \{\tau_b : \hat{F} \ge 0.05\}$.

```{r hlm-model-cs}
model_cs <- result$model_inf$model_cs
cat("95% Model Confidence Set contains", length(model_cs), "model(s):\n\n")
for (i in seq_along(model_cs)) {
  cat("  Model", i, ":", paste(model_cs[[i]], collapse = ", "), "\n")
}
cat("\nTrue model (tau_0): {1, 2, 3}\n")
```

```{r hlm-model-cs-plot, fig.cap="Candidate models and their p-values; CS = p-value ≥ 0.05", fig.height=3.5}
cand_table$In_CS <- cand_table$p_value >= 0.05
ggplot(cand_table, aes(x = factor(Model_ID), y = p_value, fill = In_CS)) +
  geom_col(color = "white", width = 0.6) +
  geom_hline(yintercept = 0.05, linetype = "dashed",
             color = "#e74c3c", linewidth = 1.1) +
  annotate("text", x = 0.7, y = 0.07, label = "α = 0.05",
           color = "#e74c3c", size = 4, hjust = 0) +
  scale_fill_manual(values = c("TRUE" = "#27ae60", "FALSE" = "#e74c3c")) +
  labs(title = "Fisher-Dempster p-values for Candidate Models",
       subtitle = "Green (p ≥ 0.05) → in 95% model confidence set",
       x = "Candidate model ID", y = "p-value", fill = "In 95% CS") +
  theme_bw(base_size = 13)
```

---

### Step 4 · Coefficient Confidence Intervals

For each regression coefficient $\beta_i$, the repro samples CI is the **union of OLS intervals**
across all models in the confidence set that contain variable $i$:

$$\Gamma_{0.95}^{\beta_i}(y_{obs}) = \bigcup_{\tau \in S^{(d)}}
  \left\{\beta_i : \hat{T}(y_{obs}, (\beta_i, \tau)) \le F^{-1}_{1,\, n-|\tau|}(0.95)\right\}$$

```{r hlm-beta-cs}
# Extract CIs for variables 1, 2, 3, 4, 5, 10 (mix of signals and zeros)
focus_vars <- c(1, 2, 3, 4, 5, 10)
beta_cs_list <- result$beta_i_cs[focus_vars]

ci_df <- do.call(rbind, lapply(seq_along(focus_vars), function(j) {
  v  <- focus_vars[j]
  ci <- as.matrix(beta_cs_list[[j]])
  if (nrow(ci) == 0) return(data.frame(var=v, lo=0, hi=0))
  data.frame(var = v, lo = min(ci[,1]), hi = max(ci[,2]))
}))

ci_df$true_beta <- beta_true[ci_df$var]
ci_df$is_signal <- ci_df$var %in% c(1, 2, 3)
ci_df$label     <- paste0("β", ci_df$var)

knitr::kable(data.frame(
  Variable   = paste0("β", ci_df$var),
  True_Value = ci_df$true_beta,
  CI_Lower   = round(ci_df$lo, 3),
  CI_Upper   = round(ci_df$hi, 3),
  Width      = round(ci_df$hi - ci_df$lo, 3),
  Covers     = ci_df$true_beta >= ci_df$lo & ci_df$true_beta <= ci_df$hi
), caption = "95% Repro Samples Confidence Intervals for Regression Coefficients")
```

```{r hlm-ci-plot, fig.cap="95% confidence intervals; red dots = true coefficient values", fig.height=4}
ggplot(ci_df, aes(x = label, color = is_signal)) +
  geom_segment(aes(y = lo, yend = hi, xend = label), linewidth = 2.5, alpha = 0.7) +
  geom_point(aes(y = true_beta), shape = 18, size = 4, color = "#e74c3c") +
  geom_hline(yintercept = 0, linetype = "dotted", color = "gray40") +
  scale_color_manual(values = c("TRUE" = "#2980b9", "FALSE" = "#95a5a6"),
                     labels = c("TRUE" = "True signal", "FALSE" = "True zero")) +
  labs(title = "95% Repro Samples Coefficient Confidence Intervals",
       subtitle = "Segments = CI range; red diamonds = true β values",
       x = "Coefficient", y = "Value", color = NULL) +
  theme_bw(base_size = 13)
```

---

# Part 3: High-Dimensional Binary Classification

**Goal:** Given $n = 100$ observations and $p = 50$ predictors with binary response $Y \in \{0,1\}$,
only 3 variables carry signal.
Construct (a) a **model confidence set** for the true active feature set $\tau_0$ and
(b) **coefficient confidence intervals** for the working logistic GLM coefficients $\boldsymbol{\beta}_{0,\tau_0}$.

**Generative model (Hou et al. 2025):**
$$Y_i = \mathbf{1}\{\mu(X_i) > U_i\}, \quad U_i \overset{iid}{\sim} \mathrm{Unif}(0,1)$$
Via the logit working model this becomes
$Y_i = \mathbf{1}\{X_{i,\tau_0}^\top\boldsymbol{\beta}_{0,\tau_0} + \varepsilon_i > 0\}$
with $\varepsilon_i \sim \mathrm{Logistic}(0,1)$.

**Same repro logic — different noise distribution:**
Just as Part 2 augments $X$ with a Gaussian noise column $u^* \sim N(0,1)$, here we augment
with a **logistic noise column** $\varepsilon^* \sim \mathrm{Logistic}(0,1)$ and run sparse logistic regression
(adaptive lasso) with the $\varepsilon^*$ column unpenalized.

---

## 3.1 Simulation Data

```{r clf-setup, cache=FALSE}
clf_path <- if (file.exists("../classification/functions.R")) {
  "../classification"
} else {
  "classification"
}
source(file.path(clf_path, "functions.R"))
library(glmnet); library(gcdnet); library(e1071); library(intervals)

with_intercept <- FALSE   # global variable required by get_tau_s
```

```{r clf-data}
set.seed(2025)
n_clf      <- 100
p_clf      <- 50
s_clf      <- 5       # sparsity constraint for working model
conf_level <- 0.95    # confidence level (α in Hou et al. notation)

beta_clf <- rep(0, p_clf)
beta_clf[c(1, 2, 3)] <- c(3, 2, 1.5)

X_clf  <- matrix(rnorm(n_clf * p_clf), n_clf, p_clf)
mu_clf <- 1 / (1 + exp(-X_clf %*% beta_clf))
Y_clf  <- as.numeric(runif(n_clf) < mu_clf)

cat("n =", n_clf, "  p =", p_clf, "  true signals: {1, 2, 3}\n")
cat("True β: β₁=3, β₂=2, β₃=1.5\n")
cat("Class balance:  Y=0:", sum(Y_clf == 0), "  Y=1:", sum(Y_clf == 1), "\n")
```

```{r clf-data-plot, fig.cap="Distribution of true logit score by class — clear separation confirms identifiable signals"}
score_df <- data.frame(
  score = as.vector(X_clf %*% beta_clf),
  Y = factor(Y_clf, labels = c("Y=0", "Y=1"))
)
ggplot(score_df, aes(x = score, fill = Y)) +
  geom_histogram(position = "identity", bins = 25, alpha = 0.6, color = "white") +
  scale_fill_manual(values = c("Y=0" = "#e74c3c", "Y=1" = "#2980b9")) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
  labs(title = "True Logit Score Distribution by Class",
       x = expression(X[1]*beta[1] + X[2]*beta[2] + X[3]*beta[3]),
       y = "Count", fill = NULL) +
  theme_bw(base_size = 14)
```

---

## 3.2 Repro Sampling — Core Steps

### Step 1 · Fisher Inversion → Model Candidate Set $\mathcal{C}$

For each repro copy $\varepsilon^{*(b)} \sim \mathrm{Logistic}(0,1)^n$, augment the design:
$$[X \mid \varepsilon^{*(b)}] \in \mathbb{R}^{n \times (p+1)}$$
Run **adaptive lasso** logistic regression with the $\varepsilon^*$ column **unpenalized**.
The selected support $\hat{\tau}(\varepsilon^{*(b)})$ estimates $\tau_0$ under that noise draw.
Collect all unique supports: $\mathcal{C} = \{\hat{\tau}(\varepsilon^{*(1)}), \ldots, \hat{\tau}(\varepsilon^{*(d)})\}$.

```{r clf-candidate, cache=TRUE, results='hide'}
set.seed(2025)
n_tau_clf <- 50   # repro draws for candidate set

epsilons_cand <- matrix(rlogis(n_clf * n_tau_clf), nrow = n_clf)
tau_candidate_clf <- get_tau_s(X_clf, Y_clf, epsilons_cand, s_clf, method = "logis adapt")
```

```{r clf-candidate-print}
cat("Repro draws d =", n_tau_clf, "\n")
cat("Unique candidate models:", length(tau_candidate_clf), "\n")
cat("Candidate model sizes:", sort(sapply(tau_candidate_clf, length)), "\n\n")

all_vars_clf <- sort(unique(unlist(tau_candidate_clf)))
cat("Variables appearing in any candidate:", paste(all_vars_clf, collapse = ", "), "\n")
```

```{r clf-candidate-plot, fig.cap="Variable selection frequency across 50 repro copies (red = true signals {1,2,3})"}
freq_clf    <- table(unlist(tau_candidate_clf))
freq_df_clf <- data.frame(Variable = as.integer(names(freq_clf)),
                           Freq     = as.integer(freq_clf))
freq_df_clf <- freq_df_clf[order(-freq_df_clf$Freq), ]
top_clf     <- head(freq_df_clf, 15)
top_clf$is_true <- top_clf$Variable %in% c(1, 2, 3)

ggplot(top_clf, aes(x = reorder(factor(Variable), Freq), y = Freq, fill = is_true)) +
  geom_col(color = "white") +
  coord_flip() +
  scale_fill_manual(values = c("TRUE" = "#e74c3c", "FALSE" = "#7f8c8d"),
                    labels = c("TRUE" = "True signal", "FALSE" = "False positive")) +
  labs(title = "Top-15 Variables by Selection Frequency (Classification)",
       subtitle = "Red = true signal variables {1, 2, 3}",
       x = "Variable index", y = paste0("Times selected (out of ", n_tau_clf, " repro copies)"),
       fill = NULL) +
  theme_bw(base_size = 13)
```

---

### Step 2 · Nuclear Mapping → Model Confidence Set

For each candidate $\tau \in \mathcal{C}$:

1. Fit logistic GLM on $(Y, X_\tau)$ to get $\hat{\boldsymbol{\beta}}_\text{MLE}$.
2. Generate $n_\text{mc}$ repro responses:
   $Y^*_i = \mathbf{1}\{X_{i,\tau}^\top\hat{\boldsymbol{\beta}}_\text{MLE} + \varepsilon^*_i > 0\}$
3. Fit lasso on each $Y^*$ to get $\hat{\tau}^*$; record its empirical distribution.
4. Nuclear statistic:
   $\widetilde{T}(\tau, \hat{\boldsymbol{\beta}}) = \hat{P}\!\left(\hat{\tau}^* \text{ more probable than } \hat{\tau}_\text{obs}\right)$

Model confidence set at level 0.95:
$$\Gamma_{0.95}^\tau = \{\tau \in \mathcal{C} : \widetilde{T}(\tau, \hat{\boldsymbol{\beta}}_\text{MLE}) \le 0.95\}$$

```{r clf-model-cs, cache=TRUE, results='hide'}
set.seed(2025)
n_mc_clf <- 100

# Lasso-selected model on observed data (reference for nuclear mapping)
fit_obs_clf  <- glmnet(X_clf, Y_clf, family = "binomial", intercept = with_intercept)
tau_obs_idx  <- max(which(fit_obs_clf$df <= s_clf))
tau_fit_obs  <- which(coef.glmnet(fit_obs_clf)[-1, tau_obs_idx] != 0)

epsilons_mc_clf <- matrix(rlogis(n_clf * n_mc_clf), nrow = n_clf)

nuclear_clf  <- numeric(length(tau_candidate_clf))
tau_cs_clf   <- list()

for (j in seq_along(tau_candidate_clf)) {
  tau    <- tau_candidate_clf[[j]]
  Data_j <- data.frame(Y = Y_clf, X_work = X_clf[, tau, drop = FALSE])
  beta_mle_j <- tryCatch(
    glm(Y ~. - 1, data = Data_j, family = binomial(link = "logit"))$coefficients,
    error = function(e) rep(0, length(tau))
  )
  nuc <- nuclear_tau_nuisance(beta_mle_j, X_clf, epsilons_mc_clf,
                               tau_fit_obs, tau, with_intercept, n_mc_clf)
  nuclear_clf[j] <- nuc
  if (nuc <= conf_level) tau_cs_clf <- c(tau_cs_clf, list(tau))
}
```

```{r clf-model-cs-print}
cat("Total candidate models:", length(tau_candidate_clf), "\n")
cat("Models in 95% confidence set:", length(tau_cs_clf), "\n\n")

for (i in seq_along(tau_cs_clf)) {
  cat("  Model", i, ": {", paste(tau_cs_clf[[i]], collapse = ", "), "}\n")
}

# Under a sparsity-s working model, the CS identifies the best s-sparse approximation.
# The true signals {1,2,3} should appear in CS models even if exact {1,2,3} is not the CS target.
any_contains_true <- any(sapply(tau_cs_clf, function(tau) all(c(1, 2, 3) %in% tau)))
cat("\nTrue signals {1,2,3} in at least one CS model:", any_contains_true, "\n")
cat("(Working model uses sparsity s =", s_clf, "— CS models contain true signals plus",
    "best-fitting additional variables.)\n")
```

```{r clf-model-cs-plot, fig.cap="Nuclear statistics per candidate model; ≤ 0.95 threshold → included in confidence set"}
nuc_df_clf <- data.frame(
  Model   = seq_along(tau_candidate_clf),
  Nuclear = nuclear_clf,
  In_CS   = nuclear_clf <= conf_level
)

ggplot(nuc_df_clf, aes(x = factor(Model), y = Nuclear, fill = In_CS)) +
  geom_col(width = 0.7, color = "white") +
  geom_hline(yintercept = conf_level, linetype = "dashed",
             color = "#e74c3c", linewidth = 1.1) +
  annotate("text", x = 0.6, y = conf_level + 0.02,
           label = "95% threshold", color = "#e74c3c", size = 4, hjust = 0) +
  scale_fill_manual(values = c("TRUE" = "#27ae60", "FALSE" = "#e74c3c"),
                    labels = c("TRUE" = "In 95% CS", "FALSE" = "Excluded")) +
  labs(title = "Nuclear Statistic per Candidate Classification Model",
       subtitle = "Models at or below 0.95 are in the 95% model confidence set",
       x = "Candidate model ID", y = expression(tilde(T)(tau)), fill = NULL) +
  theme_bw(base_size = 13)
```

---

### Step 3 · Coefficient Confidence Intervals (Wald Union)

For each $\tau$ in the model confidence set, fit logistic GLM and compute a Wald CI for $\beta_j$.
The coefficient confidence set is the **union across all models in $\Gamma_{0.95}^\tau$**:

$$\Gamma_{0.95}^{\beta_j} = \bigcup_{\tau \in \Gamma_{0.95}^\tau}
  \left\{\beta_j : |\hat{\beta}_{j,\tau} - \beta_j| \le z_{0.975}\,\hat{\sigma}_{j,\tau} / \sqrt{n}\right\}$$

```{r clf-beta-cs}
focus_vars_clf <- c(1, 2, 3, 4, 5)

if (length(tau_cs_clf) > 0) {
  beta_results_clf <- betaj_cs_wald(X_clf, Y_clf, beta_clf, tau_cs_clf, alpha = conf_level)

  ci_clf_df <- do.call(rbind, lapply(focus_vars_clf, function(j) {
    ci <- as.matrix(beta_results_clf[[j]]$conf_interval)
    if (nrow(ci) == 0 || (nrow(ci) == 1 && ci[1,1] == 0 && ci[1,2] == 0)) {
      data.frame(var = j, lo = NA, hi = NA)
    } else {
      ci_real <- ci[!(ci[,1] == 0 & ci[,2] == 0), , drop = FALSE]
      if (nrow(ci_real) == 0) data.frame(var = j, lo = NA, hi = NA)
      else data.frame(var = j, lo = min(ci_real[,1]), hi = max(ci_real[,2]))
    }
  }))
} else {
  ci_clf_df <- data.frame(var = focus_vars_clf, lo = NA, hi = NA)
}

ci_clf_df$true_beta <- beta_clf[ci_clf_df$var]
ci_clf_df$is_signal <- ci_clf_df$var %in% c(1, 2, 3)
ci_clf_df$label     <- paste0("β", ci_clf_df$var)
ci_clf_df$covers    <- !is.na(ci_clf_df$lo) &
                       ci_clf_df$true_beta >= ci_clf_df$lo &
                       ci_clf_df$true_beta <= ci_clf_df$hi

knitr::kable(data.frame(
  Variable  = ci_clf_df$label,
  True_β    = ci_clf_df$true_beta,
  CI_Lower  = round(ci_clf_df$lo, 3),
  CI_Upper  = round(ci_clf_df$hi, 3),
  Covers    = ci_clf_df$covers
), caption = "95% Repro Samples Coefficient CIs — Binary Classification (Wald union over model CS)")
```

```{r clf-ci-plot, fig.cap="95% CIs for selected classification coefficients; red diamonds = true values"}
ci_clf_plot <- ci_clf_df[!is.na(ci_clf_df$lo), ]

if (nrow(ci_clf_plot) > 0) {
  ggplot(ci_clf_plot, aes(x = label, color = is_signal)) +
    geom_segment(aes(y = lo, yend = hi, xend = label), linewidth = 2.5, alpha = 0.7) +
    geom_point(aes(y = true_beta), shape = 18, size = 4, color = "#e74c3c") +
    geom_hline(yintercept = 0, linetype = "dotted", color = "gray40") +
    scale_color_manual(values = c("TRUE" = "#2980b9", "FALSE" = "#95a5a6"),
                       labels = c("TRUE" = "True signal", "FALSE" = "True zero")) +
    labs(title = "95% Repro Samples Coefficient CIs — Binary Classification",
         subtitle = "Segments = CI range; red diamonds = true β values",
         x = "Coefficient", y = "Value", color = NULL) +
    theme_bw(base_size = 13)
} else {
  cat("No models in confidence set — increase n_tau_clf or n_mc_clf for a larger example.\n")
}
```

---

## Summary

| Method | Target Parameter | Repro Noise | Key Repro Step | Result |
|---|---|---|---|---|
| **GMM** | Unknown $K_0$ (discrete) | $u^* \sim N(0,1)$ | Fisher inversion via mixture regression $[y \sim u^*]$ | 95% CS for $K_0$ |
| **HD Linear** | Sparse model $\tau_0$ + coefficients $\beta$ | $u^* \sim N(0,1)$ | Fisher inversion via adaptive Lasso on $[X \mid u^*]$ | Model CS + coefficient CIs |
| **HD Binary** | Active feature set $\tau_0$ + GLM coefficients $\beta$ | $\varepsilon^* \sim \mathrm{Logistic}(0,1)$ | Fisher inversion via adaptive Lasso on $[X \mid \varepsilon^*]$ | Model CS + coefficient CIs |

All three methods share the same core principle:

> **Replace the unknown noise realization $u^{rel}$ with Monte-Carlo copies $u^*$**,
> invert the generative model to obtain candidate parameters,
> then use a nuclear mapping to screen which candidates are consistent
> with the observed data at level $1 - \alpha$.
